---
title: "Fetching JSON data from REST APIs"
author: "Alessandro Speranza"
date: "1/12/2021"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cash = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(rjson)
library(tibble)
library(DT)
```

<br>

# Convert JSON URLs to R Data Frame

## Data Import from JSON files
First step is converting JSON files (raw data) to lists (in these case nested lists). 

```{r, load_data}
data536 <- rjson::fromJSON(file="https://api.musement.com/api/v3/events/536.json")
data537 <- rjson::fromJSON(file="https://api.musement.com/api/v3/events/537.json")
data543 <- rjson::fromJSON(file="https://api.musement.com/api/v3/events/543.json")
data512 <- rjson::fromJSON(file="https://api.musement.com/api/v3/events/512.json")
#data285 <- rjson::fromJSON(file="https://api.musement.com/api/v3/events/285.json")
```
The last JSON file (285) is commented because is not accessible from the browser with the error:  
**{"code":"0","message":"You don't have permission to access this resource."}**

<br>

## Unlisting data from nested lists
After having created the four lists, for each list I retrieved the following info:

* **event title**
* **event price**
* **number of reviews**
<br>

```{r, unlisting_data}
# Dataset 536
data536_title <- unlist(data536[["title"]])
data536_price <- unlist(data536[["retail_price"]][["formatted_value"]])
data536_reviews_number <- unlist(data536[["reviews_number"]])

# Dataset 537
data537_title <- unlist(data537[["title"]])
data537_price <- unlist(data537[["retail_price"]][["formatted_value"]])
data537_reviews_number <- unlist(data537[["reviews_number"]])

# Dataset 543
data543_title <- unlist(data543[["title"]])
data543_price <- unlist(data543[["retail_price"]][["formatted_value"]])
data543_reviews_number <- unlist(data543[["reviews_number"]])

# Dataset 512
data512_title <- unlist(data512[["title"]])
data512_price <- unlist(data512[["retail_price"]][["formatted_value"]])
data512_reviews_number <- unlist(data512[["reviews_number"]])
```

<br>

## Creating the final data frame
As final step, I created a data frame which collects the data in a tidy format.

```{r, create_final_dataset}
final_dataset <- tribble(
  ~id, ~title, ~price, ~reviews,
  "536", data536_title, data536_price, data536_reviews_number,
  "537", data537_title, data537_price, data537_reviews_number,
  "543", data543_title, data543_price, data543_reviews_number,
  "512", data512_title, data512_price, data512_reviews_number
)

## Export the final_dataset on file system using readr package 
write_csv(final_dataset, "final_dataset.csv")
```

<br>

## Displaying & Exporting data

```{r, displaying_data, echo = FALSE, message = FALSE, warning = FALSE}
 sketch <- htmltools::withTags(table(
   tableHeader(colnames(final_dataset))
 ))

 DT::datatable(final_dataset,
               extensions = c('KeyTable','Buttons','Scroller','ColReorder'),
               container = sketch,
               options = list(dom = 'Bfrtip',
                              buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                              deferRender = TRUE,
                              scrollY = 420,
                              scroller = TRUE,
                              colReorder = TRUE,
                              keys = TRUE),
               rownames = FALSE,
               filter = list(position = 'top', clear = FALSE, plain = TRUE)
 )
```
